A performance comparison of Dask and Spark for data-intensive neuroimaging pipelines

### 2019-07-27 latex/paper.tex

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{times}
\usepackage[binary-units=true]{siunitx}
\usepackage{latexsym}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=blue,filecolor=black,urlcolor=blue}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{dblfloatfix}

@@

 Our second application calculates the histogram of the BigBrain image (see
 Algorithm~\ref{alg:histogram}). It reads the image blocks from the shared file
 system, calculates intensity frequencies, aggregates the frequencies across the
 blocks, and finally writes the resulting histogram to the shared file system as a
 single \SI{766}{\kilo\byte} file. This application implements a typical map-reduce
 program, where the final result is obtained from all the input blocks (see
 Fig.~\ref{fig:tg-histo}). This application requires data shuffling, incurring 
 additional performance costs compared to Algorithm~\ref{alg:incrementation}.
 The total amount of shuffled data is, however, limited to
 \SI{2.62}{\mega\byte} per blocks as it only consists of image histograms.

@@

For each run, we measured the application makespan as well as the cumulative 
data read, compute, data write, and engine overhead across all application tasks. 
We measured the overhead by

% \TG{\ldots, maybe add a figure}. \MD{Done but might need
% adjustment depending on how the overhead is calculate (idle vs wasted)}

% \TG{explain that number of iterations may impact futures.}

The baseline for our experiments is: 8 workers, 125 blocks, 10 iterations and 4
seconds sleep delay.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{times}
\usepackage[binary-units=true]{siunitx}
\usepackage{latexsym}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=blue,filecolor=black,urlcolor=blue}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{caption}
\usepackage{subcaption}

@@

 Our second application calculates the histogram of the BigBrain image (see
 Algorithm~\ref{alg:histogram}). It reads the image blocks from the shared file
 system, calculates intensity frequencies, aggregates the frequencies across the
 blocks, and finally writes the resulting histogram to the shared file system as a
 single \SI{766}{\kilo\byte} file. This application implements a typical map-reduce
 program, where the final result is obtained from all the input blocks (see
 Fig.~\ref{fig:tg-histo}). This application requires data shuffling, incurring 
 additional performance costs compared to Algorithm~\ref{alg:incrementation}.
 The total amount of shuffled data is, however, limited to
 \SI{2.62}{\mega\byte} per blocks as it only consists of image histograms.
Two implementation are studied: pure Python and NumPy.

@@

For each run, we measured the application makespan as well as the cumulative 
data read, compute, data write, and engine overhead across all application tasks. 
The overhead calculation for each CPU is the end time of its last processed task
minus the start time of the application; the summation of those results is the total
overhead.

% The baseline for our experiments is: 8 workers, 125 blocks, 10 iterations and 4
% seconds sleep delay.
